Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-13 ehp_revision/writing/ehp_discussion.tex
Continue work on revisions

The open-source data generally correspond well with data from other potential
sources (Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison}), but
there are caveats. The rainfall data are generally well-correlated with
ground-based observations, but may sometimes underestimate very high rainfall
values (Figure~\ref{fig:raincomparison}), and in some counties the correlation
was substantially lower when considering only tropical cyclones with cumulative
local rainfall of 75 mm or more (Supplemental Table 1). When rainfall data is
used to create binary exposure classifications, this disagreement is unlikely
to influence results, as both data sources agree in identifying these as storms
with high rainfall, but would be important to consider for cases that include
rainfall as a continuous measurement.

@@

\textbf{This dataset is limited to the contiguous US. The precipitation data is
extracted and aggregated to the county level from a re-analysis data product.
While the re-analysis product used here (NLDAS-2) only covers the contiguous
US, other similar re-analysis products, as well as other types of precipitation
datasets, have global coverage \parencite{sun2018review}. The wind data are
generated based on a model that is currently US-focused
\parencite{stormwindmodel}, but could be extended to other areas, although this
would require adding new land/sea masks within the associated software, as well
as accounting for differences across storm basins in wind averaging periods
\parencite{harper2010guidelines} and in the direction of cyclonic winds in the
Northern versus Southern Hemisphere. Further, since the core of the wind model
was developed based on data from Atlantic-basin storms
\parencite{willoughby2006parametric}, an extension to other areas should
include separate validation and calibration to ensure it performs appropriately
in those settings. Alternatively, other wind field modeling software is
available that provides a global coverage, like Geoscience Australia's Tropical
Cyclone Risk Model (http://geoscienceaustralia.github.io/tcrm/). For tornado
and flood events, the data described in this paper drew on a US-focused storm
events database, and so international extension of data on these hazards would
require access to similar databases covering other countries. Finally, the
relevant geopolitical boundaries to use for aggregation would vary by country
(e.g., municipalities in Mexico, districts in India).}

\textbf{The dataset we present focuses on the physical hazards of a tropical
cyclone.  However, health impacts will often some through indirect pathways,
including through damage to property and infrastructure. In future work, it
would be useful to expand this dataset to add data related to these pathways,
to allow research exploring the role of indirect pathways from tropical cyclone
phyiscal hazards to health risk. This expansion could include adding data on
normalized storm-associated damages, or proxy measurements of such damages,
from sources like the US NOAA's Storm Events database and the US Federal
Emergency Management Agency's county-level disaster declarations.}

@@

Based on our results, the use of a distance-based metric to assess exposure to
any of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often introduce exposure
misclassification \textbf{(Tables S3--S6)}. This conclusion reinforces
similar findings from a study of Florida's 2004 storm
season~\parencite{grabich2015measuring}.  For some studies, such exposure
misclassification might plausibly be differential.  For example, tropical
cyclone wind exposures tend to be concentrated in counties near the coast,
while tropical cyclone rain exposures sometimes extend well inland.  If the
etiologically-relevant exposure for a health outcome is extreme rainfall but
exposure is classified based on measurements of wind, the probability of being
misclassified as unexposed would be higher in inland counties, while the
probability of being misclassified as exposed would be higher in coastal
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, exposure
misclassification would be differential~\parencite{savitz2016interpreting}.
Such differential exposure misclassification could bias estimates of tropical
cyclone effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\parencite{savitz2016interpreting,
armstrong1998effect}.

@@

Second, these data are aggregated to the county level. \textbf{This spatial
scale allows for easy integration with health outcome data aggregated at the
county level. Such data is often used for disaster epidemiology, as aggregated
data may be easier to access than individual-level data, especially at a scale
that covers many locations and a long time period and so allows higher
statistical power and a broader range of exposure levels within the study
\parencite{wakefield2008overcoming}.}

\textbf{These ecological exposure estimates, however, set a common exposure
level throughout the county, ignoring within-county variability, even though
such variability often exists. For some hazards, this within-county variation
in exposure level could be stark. For example, tornadoes cause very localized
damage, directly along the tornado's path---a tornado can destroy homes on one
side of a street while leaving those on the opposite side untouched. Levels of
other hazards, like storm-associated winds and rain, will also vary within a
county, but typically with smoother variation. In particular, it will be
unlikely that a county will have one area that is exposed to extremes of these
hazards from a tropical cyclone while other parts of the county are completely
unexposed, as both the wind fields and rain fields of tropical cyclones tend to
be large in comparison to the size of a county.}

\textbf{Aggregated data can be used to infer contextual level
associations---for example, the association between county-level exposure to a
storm hazard and county-wide rates of a health outcome. However, ecological
data is also sometimes used to infer individual-level associations (e.g., the
association between personal exposure to a storm hazard and personal risk of
experiencing the health outcome). Individual-level inference from
ecological/aggregated data is susceptible to ecological bias
\parencite{greenland1994invited, portnov2007ecological, idrovo2011three}.
Researchers who use the data provided here for ecological studies---with the
aim of making individual-level inferences---should be aware of this potential
and could explore approaches for minimizing risk of ecological bias (e.g.,
\cite{wakefield2008overcoming}).}

>>>>

The open-source data generally correspond well with data from other potential
sources (Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison}), but
there are caveats. The rainfall data are generally well-correlated with
ground-based observations, but may sometimes underestimate very high rainfall
values (Figure~\ref{fig:raincomparison}), \textbf{and in some counties the
correlation was substantially lower when considering only tropical cyclones
with cumulative local rainfall of 75 mm or more (Supplemental Table 1).} When
rainfall data is used to create binary exposure classifications, this
disagreement is unlikely to influence results, as both data sources agree in
identifying these as storms with high rainfall, but would be important to
consider for cases that include rainfall as a continuous measurement.

@@

\textbf{This dataset is limited to the contiguous US, and while expansion to
global coverage would be useful and feasible, there would be some challenges.
For precipitation data, the re-analysis product used here (NLDAS-2) only covers
the contiguous US, although other re-analysis products, as well as other types
of precipitation datasets, have global coverage \parencite{sun2018review}. The
wind data are generated based on a model that is currently US-focused
\parencite{stormwindmodel}, but could be extended to other areas, although this
would require adding new land/sea masks within the associated software, as well
as accounting for differences across storm basins in wind averaging periods
\parencite{harper2010guidelines} and in the direction of cyclonic winds in the
Northern versus Southern Hemisphere. Further, since the core of the wind model
was developed based on data from Atlantic-basin storms
\parencite{willoughby2006parametric}, an extension to other areas should
include separate validation and calibration to ensure it performs appropriately
in those settings. Alternatively, other wind field modeling software is
available that provides a global coverage, like Geoscience Australia's Tropical
Cyclone Risk Model (http://geoscienceaustralia.github.io/tcrm/). For tornado
and flood events, the data described in this paper drew on a US-focused storm
events database, and so international extension of data on these hazards would
require access to similar databases covering other countries. Finally, the
relevant geopolitical boundaries to use for aggregation would vary by country
(e.g., municipalities in Mexico, districts in India).}

\textbf{The dataset we present focuses on the physical hazards of a tropical
cyclone. However, health impacts will often come through indirect pathways,
including through damage to property and infrastructure. In future work, it
would be useful to expand this dataset to add data related to these pathways,
to allow research exploring the role of indirect pathways from tropical cyclone
phyiscal hazards to health risk. This expansion could include adding data on
normalized storm-associated damages, or proxy measurements of such damages,
from sources like the US NOAA's Storm Events database and the US Federal
Emergency Management Agency's county-level disaster declarations.}

@@

Based on our results, the use of a distance-based metric to assess exposure to
any of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often introduce exposure
misclassification \textbf{(Figure \ref{fig:jaccard}, Tables S3--S6)}. This
conclusion reinforces similar findings from a study of Florida's 2004 storm
season~\parencite{grabich2015measuring}.  For some studies, such exposure
misclassification might plausibly be differential.  For example, tropical
cyclone wind exposures tend to be concentrated in counties near the coast,
while tropical cyclone rain exposures sometimes extend well inland.  If the
etiologically-relevant exposure for a health outcome is extreme rainfall but
exposure is classified based on measurements of wind, the probability of being
misclassified as unexposed would be higher in inland counties, while the
probability of being misclassified as exposed would be higher in coastal
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, exposure
misclassification would be differential~\parencite{savitz2016interpreting}.
Such differential exposure misclassification could bias estimates of tropical
cyclone effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\parencite{savitz2016interpreting,
armstrong1998effect}.

@@

Second, these data are aggregated to the county level. \textbf{This spatial
scale allows for easy integration with health outcome data aggregated at the
county level. Such data is often used for disaster epidemiology, as aggregated
data may be easier to access than individual-level data, especially at a scale
that covers many locations and years and so allows higher statistical power and
includes a broader range of exposure levels
\parencite{wakefield2008overcoming}.}

\textbf{Such ecological exposure assessment, however, sets a common exposure
level throughout the county, ignoring within-county variability, even though
such variability exists. For some hazards, this within-county variation could
be stark. For example, tornadoes cause very localized damage, directly along
the tornado's path---a tornado can destroy homes on one side of a street while
leaving those on the opposite side untouched. Levels of other hazards, like
storm-associated winds and rain, will also vary within a county, but typically
with smoother variation. In particular, it will be unlikely that a county will
have one area that is exposed to extremes of these hazards while other parts of
the county are completely unexposed, as both the wind fields and rain fields of
tropical cyclones tend to be large in comparison to the size of a county.}

\textbf{Aggregated data can be used to infer contextual-level
associations---for example, the association between county-level exposure to a
storm hazard and county-wide rates of a health outcome. However, ecological
data is also sometimes used to infer individual-level associations (e.g., the
association between personal exposure to a storm hazard and personal risk of
experiencing the health outcome). Individual-level inference from
ecological/aggregated data is susceptible to ecological bias
\parencite{greenland1994invited, portnov2007ecological, idrovo2011three}.
Researchers who use the data provided here for ecological studies---with the
aim of making individual-level inferences---should be aware of this potential
and could explore approaches for minimizing risk of ecological bias (e.g.,
\cite{wakefield2008overcoming}).}

### 2020-09-13 ehp_revision/writing/ehp_figures.tex
Work some more on revisions
Continue work on revisions

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{windcomparison}
	\caption{Comparison of two sources of wind exposure estimates: 
	(1) modeled peak sustained surface wind 
	and (2) estimates based on \ac{HURDAT2}'s wind speed radii.
	Each point represents a storm, with the x-axis giving the percent of
	counties classified in the same category of peak sustained surface
	wind ($<$34~kt; 34\,--\,49.9~kt;
	50\,--\,63.9~kt; $\ge$64~kt) by both sources of 
	data. The color of each point gives the number of study counties that were exposed to
	peak sustained surface wind of at least 34~kt (based
	on modeled wind). Estimates are shown for study storms since
	2004, the earliest year for which post-storm reanalysis wind speed
	radii are routinely available in \ac{HURDAT2}, and for which at
	least one study county had a peak sustained wind of $\ge$34~\si{\knot}
	based on the post-storm wind radii.
	}
\label{fig:windcomparison}
\end{figure}

@@

\begin{figure}%[tbhp] 
	\centering 
	\includegraphics[width = 0.8\linewidth]{jaccard_heatmap.pdf}
	\caption{Agreement between exposure
	classifications based on different single-hazard exposure metrics for all storms
	between~1996 and~2011 for which at least~100 counties were exposed
	based on at least one metric.  Each row shows one storm, and the color
	of each cell shows the measured Jaccard index for each pair of exposure
	metrics (proportion of counties classified as exposed by both metrics
	out of counties classified as exposed by either metric). For 
	Grace in 2003 and Ida in 2009, there were no county exposures for
	either the tornado-based metric or the wind-based metric (indicated 
	by gray squares). Colors to the right of the
	heatmap show the number of exposed counties
	based on any of the metrics. Storms are displayed
	within clusters that have similar patterns based on hierarchical 
	clustering.}
\label{fig:jaccard} 
\end{figure}

>>>>

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{windcomparison}
	\caption{Comparison of two sources of wind exposure estimates: 
	(1) modeled peak sustained surface wind 
	and (2) estimates based on \ac{HURDAT2}'s wind speed radii.
	Each point represents a storm, with the x-axis giving the percent of
	counties classified in the same category of peak sustained surface
	wind ($<$34~kt; 34\,--\,49.9~kt;
	50\,--\,63.9~kt; $\ge$64~kt) by both sources of 
	data. The color of each point gives the number of study counties that were exposed to
	peak sustained surface wind of at least 34~kt (based
	on modeled wind). Estimates are shown for study storms since
	2004, the earliest year for which post-storm reanalysis wind speed
	radii are routinely available in \ac{HURDAT2}, and for which at
	least one study county had a peak sustained wind of $\ge$34~kt
	based on the post-storm wind radii.
	}
\label{fig:windcomparison}
\end{figure}

@@

\begin{figure}%[tbhp] 
	\centering 
	\includegraphics[width = 0.8\linewidth]{jaccard_heatmap.pdf}
	\caption{Agreement between exposure classifications based on different
	single-hazard exposure metrics for all storms between~1996 and~2011 for
	which at least~100 counties were exposed based on at least one metric.
	Each row shows one storm, and the color of each cell shows the measured
	Jaccard index for each pair of exposure metrics (proportion of counties
	classified as exposed by both metrics out of counties classified as
	exposed by either metric). For Grace in 2003 and Ida in 2009, there
	were no county exposures for either the tornado-based metric or the
	wind-based metric (indicated by gray squares). Colors to the right of
	the heatmap show the number of exposed counties based on any of the
	metrics, \textbf{and this panel is linked with the color scale labeled ``\# of
	counties exposed by any metric''.} Storms are displayed within clusters
	that have similar patterns based on hierarchical clustering.}
\label{fig:jaccard} 
\end{figure}

### 2020-09-13 ehp_revision/writing/ehp_methods.tex
Continue work on revisions

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at four standardized times for weather data collection (synoptic times),
6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}.  We interpolated this
position to~15-\si{\minute} intervals using natural cubic spline
interpolation~\parencite{hurricaneexposure}. At each~15-\si{\minute} interval,
we measured the distance between the storm's center and each county's
population mean center, \textbf{as of the 2010 US Decennial
Census}~\parencite{countycenters}. We took the minimum distance for each county
as a measure of how close the storm came to the county over its lifetime.  We
also recorded the time when this occurred for each county so we could later
link observed data on precipitation, flooding, and tornadoes.  To allow
matching with data recorded in local time (e.g., health data), we converted
these times from \ac{UTC} to local time~\parencite{countytimezones}.

@@

The tornado observations from this dataset---\textbf{along with the derived
version of the data available through the Storm Prediction Center's National
Tornado Database~\parencite{center2020storm}---are the official tornado event
data} for the \ac{US}. \textbf{There are no other collections of tornado data
comparable in emporal or geographic scope,} and so we did not further validate
the tornado event data. It is difficult to characterize flooding at the county
level because flooding can be very localized and can be triggered by a variety
of causes. To investigate the extent to which the NOAA flood event listings
capture extremes that might be identified with other flooding data sources, we
investigated a sample of study counties, comparing the flood event data during
tropical storms with streamflow measurements at \ac{US} Geological Survey
county streamflow gages \parencite{usgsgages, countyfloods, dataRetrieval}.  We
considered nine study counties, selecting counties geographically spread
through storm-prone areas of the eastern \ac{US} and with at least one
streamflow gage reporting data during all events. The sample counties were:
Baltimore County, MD; Bergen County, NJ; Escambia County, FL; Fairfield County,
CT; Fulton County, GA; Harris County, TX; Mobile County, AL; Montgomery County,
PA; and Wake County, NC.

@@

Finally, we investigated how well exposure assessment agreed across these
metrics. \textbf{These results can help epidemiologists answer several key
questions as they interpret previous research and design new studies. For
example, if a single storm hazard has been used to measure exposure in an
epidemiological study, can the result be interpreted as an association with
tropical cyclone exposure in general, or should it be limited to represent an
association with that specific storm hazard? If a study investigates the
association between a single storm hazard and a health outcome, could this
estimate be confounded by other storm hazards? When planning a new study that
will incorporate several storm hazards in a mixtures approach, will there
likely be numerical problems in fitting the model from multicollinearity, or
difficulties in disentangling the role of separate hazards?}

>>>>

We first measured how close each storm's central track came to each county. We
used tracking data from \ac{HURDAT2}, which records the storm center's position
at \textbf{four standardized times for weather data collection (synoptic
times)}, 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am \ac{UTC}.  We interpolated
this position to~15-\si{\minute} intervals using natural cubic spline
interpolation~\parencite{hurricaneexposure}. At each~15-\si{\minute} interval,
we measured the distance between the storm's center and each county's
population mean center, \textbf{as of the 2010 US Decennial
Census}~\parencite{countycenters}. We took the minimum distance for each county
as a measure of how close the storm came to the county over its lifetime.  We
also recorded the time when this occurred for each county so we could later
link observed data on precipitation, flooding, and tornadoes.  To allow
matching with data recorded in local time (e.g., health data), we converted
these times from \ac{UTC} to local time~\parencite{countytimezones}.

@@

The tornado observations from this dataset---\textbf{along with the derived
version of the data available through the Storm Prediction Center's National
Tornado Database~\parencite{center2020storm}---are the official tornado event
data} for the \ac{US}. \textbf{There are no other collections of tornado data
comparable in temporal or geographic scope,} and so we did not further validate
the tornado event data. It is difficult to characterize flooding at the county
level because flooding can be very localized and can be triggered by a variety
of causes. To investigate the extent to which the NOAA flood event listings
capture extremes that might be identified with other flooding data sources, we
investigated a sample of study counties, comparing the flood event data during
tropical storms with streamflow measurements at \ac{US} Geological Survey
county streamflow gages \parencite{usgsgages, countyfloods, dataRetrieval}.  We
considered nine study counties, selecting counties geographically spread
through storm-prone areas of the eastern \ac{US} and with at least one
streamflow gage reporting data during all events. The sample counties were:
Baltimore County, MD; Bergen County, NJ; Escambia County, FL; Fairfield County,
CT; Fulton County, GA; Harris County, TX; Mobile County, AL; Montgomery County,
PA; and Wake County, NC.

@@

Finally, we investigated how well exposure assessment agreed across these
metrics. \textbf{These results can help epidemiologists answer several key
questions as they interpret previous research and design new studies. For
example, if a single storm hazard has been used to measure exposure in an
epidemiological study, can the result be interpreted as an association with
tropical cyclone exposure in general, or should it be limited to represent an
association with that specific storm hazard? If a study investigates the
association between a single storm hazard and a health outcome, could this
estimate be confounded by other storm hazards? When planning a new study that
will incorporate several storm hazards, might there be variance inflation from
multicollinearity or difficulties in disentangling the roles of separate
hazards?}

### 2020-09-13 ehp_revision/writing/ehp_results.tex
Continue work on revisions

We explored potential limitations in these data by comparing them with data
from other available sources.  For estimates of storm-associated rainfall, we
compared data in the open-source package with ground-based
observations in nine sample counties (Figure~\ref{fig:raincomparison}). Within
these counties, storm-related rainfall measurements were well-correlated
between the two data sources, with rank correlations (bottom right of each
graph in Figure~\ref{fig:raincomparison}) between 0.87 and 0.98. 
There was some evidence that our primary rainfall metric may tend to
underestimate rainfall totals in storms with extremely high rainfall, based on
a few heavy-rainfall storms in Harris County, TX, Mobile County, AL, Charleston
County, SC, and Wake County, NC (Figure~\ref{fig:raincomparison}). However,
even in these cases, it was rare for a storm to be classified differently
(under the precipitation threshold of 75~\si{\milli\metre} we used for binary
exposure classification for later analysis) based on the source of
precipitation data. Horizontal and vertical lines in each small plot in
Figure~\ref{fig:raincomparison} show the threshold of 75~\si{\milli\metre}, so
storms in the lower left and upper right quadrants would be classified the same
(``exposed'' or ``unexposed'') regardless of the precipitation data source,
while storms in the upper left and lower right quadrants would be classified
differently. Such cases were rare.

@@

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}; \textbf{Tables S3--S6 provide underlying
numbers for the most extensive of these, the storms for which 250 of more
counties were exposed based on at least one metric}). In this figure, each row
provides results for one tropical cyclone, and each box in that row shows the
Jaccard coefficient for a pair of metrics. For all pairs of metrics, agreement
in exposure assessment was, at best, moderate for all but a few storms. When
comparing distance- and wind-based exposure assessment, only about 10\% of
storms had Jaccard indices higher than 0.6 (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
more were assessed the same under both metrics). For comparisons of assessments
based on other combinations of distance-, wind-, rain-, and flood-based
metrics, fewer than 5\% of storms had Jaccard indices above 0.6.  The
tornado-based metric had universally poor agreement with other metrics in
county-level classification across the tropical cyclones considered.

>>>>

We explored potential limitations in these data by comparing them with data
from other available sources.  For estimates of storm-associated rainfall, we
compared data in the open-source package with ground-based observations in nine
sample counties (Figure~\ref{fig:raincomparison}). Within these counties,
storm-related rainfall measurements were well-correlated between the two data
sources, with rank correlations (bottom right of each graph in
Figure~\ref{fig:raincomparison}) between 0.87 and 0.98.  There was some
evidence that our primary rainfall metric may tend to underestimate rainfall
totals in storms with extremely high rainfall, based on a few heavy-rainfall
storms in Harris County, TX, Mobile County, AL, Charleston County, SC, and Wake
County, NC (Figure~\ref{fig:raincomparison}). \textbf{Further, in some
counties, the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of 75 mm or more (Supplemental
Table 1).} However, even in these cases, it was rare for a storm to be
classified differently (under the precipitation threshold of
75~\si{\milli\metre} we used for binary exposure classification for later
analysis) based on the source of precipitation data. Horizontal and vertical
lines in each small plot in Figure~\ref{fig:raincomparison} show the threshold
of 75~\si{\milli\metre}, so storms in the lower left and upper right quadrants
would be classified the same (``exposed'' or ``unexposed'') regardless of the
precipitation data source, while storms in the upper left and lower right
quadrants would be classified differently. Such cases were rare.

@@

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}; \textbf{for the most extensive of these, storms for
which 250 of more counties were exposed based on at least one metric, Tables
S3--S6 provide underlying numbers comparing exposure assessments for the
distance-based proxy to each hazard-based metric}). In \textbf{Figure 7}, each row
provides results for one tropical cyclone, and each box in that row shows the
Jaccard coefficient for a pair of metrics. For all pairs of metrics, agreement
in exposure assessment was, at best, moderate for all but a few storms. When
comparing distance- and wind-based exposure assessment, only about 10\% of
storms had Jaccard indices higher than 0.6 (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
more were assessed the same under both metrics). For comparisons of assessments
based on other combinations of distance-, wind-, rain-, and flood-based
metrics, fewer than 5\% of storms had Jaccard indices above 0.6.  The
tornado-based metric had universally poor agreement with other metrics in
county-level classification across the tropical cyclones considered.
